sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-03 doc/paper.Rmd
movign things + couple edits

Geostatistical GLMMs (generalized linear mixed effects models) with spatially correlated random effects are a class of models appropriate for these data.
Similarly to how random intercepts can account for correlation among groups (e.g., plants counted in plots of land), spatial/spatiotemporal random effects can account for unmeasured variables causing observations to be correlated in space or space and time.
A common approach to modelling such random effects is with Gaussian random fields (GRFs), where the random effects are assumed drawn from a multivariate normal distribution, constrained by some covariance function such as the exponential or Matérn [@cressie1993; @diggle1998; @chiles1999].

@@

>>>>

Geostatistical GLMMs (generalized linear mixed effects models) with spatially correlated random effects are a class of models appropriate for these data.
Similarly to how random intercepts can account for correlation among groups (e.g., plants counted in plots of land), spatial/spatiotemporal random effects can account for unmeasured variables causing observations to be correlated in space or space and time.
A common approach to modelling these spatial effects is with Gaussian random fields (GRFs), where the random effects describing the spatial patterning are assumed drawn from a multivariate normal distribution, constrained by some covariance function such as the exponential or Matérn [@cressie1993; @diggle1998; @chiles1999].

@@

<!-- Paragraph on advanced options here?
Specifically, this could address
- PC-priors -- and other penalized priors
- Non-linear stuff / etc
- Linkages to Rstan
- Simulation
-->
